Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-29 bbbq_article.tex
Add bracket, thanks Geert
Use Meld to be (more) sure versions match

Also, for single- and multi-spanners, 
we determined the relevance of this finding by
calculating how much less SNPs are found in TMHs
when compared to soluble regions,
as depicted in figure \ref{fig:conservation_per_spanner}.
In effect, per 1,000 SNPs found in soluble protein domains, 
one finds 978 SNPs in TMHs 
of single-spanners
and 911 SNPs in TMHs of multi-spanners.

@@

We thank the Center for Information Technology of the University 
of Groningen for its support and for providing access to the Peregrine 
high performance computing cluster. 
FB is funded by a Veni grant from the Netherlands Organization for Scientific
Research (016.Veni.192.026) and an Off-Road Grant from the Dutch Medical Science Foundation (ZonMW 04510011910005).
GvdB is funded by a Young Investigator Grant from 
the Human Frontier Science Program (HFSP; RGY0080/2018), 
and a Vidi grant from 
the Netherlands Organization for Scientific Research (NWO-ALW VIDI 864.14.001). 
GvdB has received funding from the European Research Council (ERC) 
under the European Union’s Horizon 2020 research and 
innovation programme (grant agreement No. 862137.

>>>>

Also, for single- and multi-spanners, we determined the
relevance of this finding by calculating where and how much less SNPs
are found in TMHs when compared to soluble regions, as
depicted in Figure \ref{fig:conservation_per_spanner} 
and \ref{fig:conservation_per_spanner}.
In effect, per 1,000 SNPs found in soluble protein domains, 
one finds 978 SNPs in TMHs 
of single-spanners
and 911 SNPs in TMHs of multi-spanners.

@@

We thank the Center for Information Technology of the University 
of Groningen for its support and for providing access to the Peregrine 
high performance computing cluster. 
FB is funded by a Veni grant from the Netherlands Organization for Scientific
Research (016.Veni.192.026) and an Off-Road Grant from the Dutch Medical Science Foundation (ZonMW 04510011910005).
GvdB is funded by a Young Investigator Grant from 
the Human Frontier Science Program (HFSP; RGY0080/2018), 
and a Vidi grant from 
the Netherlands Organization for Scientific Research (NWO-ALW VIDI 864.14.001). 
GvdB has received funding from the European Research Council (ERC) 
under the European Union’s Horizon 2020 research and 
innovation programme (grant agreement No. 862137).

### 2021-12-29 frontiers.tex
Add bracket, thanks Geert
Use Meld to be (more) sure versions match

This study had two objectives. 
First, we aimed to generalize our findings by predicting
the antigenic presentation
from different kingdoms of life in both MHC-I and -II. 
From these \emph{in silico} predictions, we conclude that TMH-derived
epitopes from a human, viral and bacterial proteome
are likely to be presented more often than expected by chance 
for most alleles of MHC-I and II. 
We confirmed the presentation of TMH-derived peptides 
by re-analysis of peptides from The Immune Epitope Database (IEDB) \citep{vita2019immune}.
Second, we tested our hypothesis that TMHs 
are more evolutionary conserved than soluble protein regions.
Our analysis of human single nucleotide polymorphisms (SNPs) showed 
that random point mutations are indeed less likely
to occur within TMHs. 
These findings strengthen the emerging notion 
that TMHs are important for the T cell-mediated adaptive immune system, 
and hence are of  
overlooked importance in vaccine development.

@@

To obtain experimental confirmation that peptides stemming from TMHs 
are presented by MHC-I and MHC-II,
we mined the IEDB \citep{vita2019immune}
for confirmed human MHC-ligands.
We queried the IEDB for all linear epitopes obtained
from MHC ligand assays in healthy humans, 
carrying the MHC alleles as used in this study.
From these epitopes, we kept those that were present
exactly once in the human reference proteome
with UniProt ID UP000005640\_9606.
We concluded that the epitope overlapped with a TMH if at least 1 amino acid was overlapping with a TMH, as predicted with \verb;TMHMM; \cite{krogh2001predicting}.

The full analysis can be found
at \url{https://github.com/richelbilderbeek/bbbq_article_issue_157}.

@@

%
% Frontiers text, just keep it in for now to be sure.
%
%\section{Article types}
%
% For requirements for a specific article type please refer to the Article Types on any Frontiers journal page. Please also refer to  \href{http://home.frontiersin.org/about/author-guidelines#Sections}{Author Guidelines} for further information on how to organize your manuscript in the required sections or their equivalents for your field
%
% For Original Research articles, please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.
%
%\section{Manuscript Formatting}
%
%\subsection{Heading Levels}
%
%There are 5 heading levels
%
%\subsection{Level 2}
%\subsubsection{Level 3}
%\paragraph{Level 4}
%\subparagraph{Level 5}
%
%\subsection{Equations}
%Equations should be inserted in editable format from the equation editor.
%
%\begin{equation}
%\sum x+ y =Z\label{eq:01}
%\end{equation}
%
%\subsection{Figures}
%Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript. Figures will then be automatically embedded at the bottom of the submitted manuscript. Kindly ensure that each table and figure is mentioned in the text and in numerical order. Figures must be of sufficient resolution for publication \href{http://home.frontiersin.org/about/author-guidelines#ResolutionRequirements}{see here for examples and minimum requirements}. Figures which are not according to the guidelines will cause substantial delay during the production process. Please see \href{http://home.frontiersin.org/about/author-guidelines#GeneralStyleGuidelinesforFigures}{here} for full figure guidelines. Cite figures with subfigures as figure \ref{fig:2}B.
%
%
%\subsubsection{Permission to Reuse and Copyright}
%Figures, tables, and images will be published under a Creative Commons CC-BY licence and permission must be obtained for use of copyrighted material from other sources (including re-published/adapted/modified/partial figures and images from the internet). It is the responsibility of the authors to acquire the licenses, to follow any citation instructions requested by third-party rights holders, and cover any supplementary charges.
%%Figures, tables, and images will be published under a Creative Commons CC-BY licence and permission must be obtained for use of copyrighted material from other sources (including re-published/adapted/modified/partial figures and images from the internet). It is the responsibility of the authors to acquire the licenses, to follow any citation instructions requested by third-party rights holders, and cover any supplementary charges.
%
%\subsection{Tables}
%Tables should be inserted at the end of the manuscript. Please build your table directly in LaTeX.Tables provided as jpeg/tiff files will not be accepted. Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space. These tables will be published as \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} on the online article page at the time of acceptance. The author will be notified during the typesetting of the final article if this is the case. 
%
%\section{Nomenclature}
%
%\subsection{Resource Identification Initiative}
%To take part in the Resource Identification Initiative, please use the corresponding catalog number and RRID in your current manuscript. For more information about the project and for steps on how to search for an RRID, please click \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}{here}.
%
%\subsection{Life Science Identifiers}
%Life Science Identifiers (LSIDs) for ZOOBANK registered names or nomenclatural acts should be listed in the manuscript before the keywords. For more information on LSIDs please see \href{http://www.frontiersin.org/about/AuthorGuidelines#InclusionofZoologicalNomenclature}{Inclusion of Zoological Nomenclature} section of the guidelines.
%
%
%\section{Additional Requirements}
%
%For additional requirements for specific article types and further information please refer to \href{http://www.frontiersin.org/about/AuthorGuidelines#AdditionalRequirements}{Author Guidelines}.
%

@@

%All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to confirm the following statement:

@@

% The Author Contributions section is mandatory for all articles, including articles by sole authors. If an appropriate statement is not provided on submission, a standard one will be inserted during the production process. The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work. Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.

@@

% Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.

FB is funded by a Veni grant from the Netherlands Organization for Scientific
Research (016.Veni.192.026) and an Off-Road Grant from the Dutch Medical Science Foundation (ZonMW 04510011910005).
GvdB is funded by a Young Investigator Grant from 
the Human Frontier Science Program (HFSP; RGY0080/2018), 
and a Vidi grant from 
the Netherlands Organization for Scientific Research (NWO-ALW VIDI 864.14.001). 
GvdB has received funding from the European Research Council (ERC) 
under the European Union’s Horizon 2020 research and 
innovation programme (grant agreement No. 862137.

@@

% This is a short text to acknowledge the contributions of specific colleagues, institutions, or agencies that aided the efforts of the authors.

@@

\section*{Supplemental Data}
 \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.

>>>>

This study had two objectives. 
First, we aimed to generalize our findings by predicting
the antigenic presentation
from different kingdoms of life in both MHC-I and -II. 
From these \emph{in silico} predictions, we conclude that TMH-derived
epitopes from a human, viral and bacterial proteome
are likely to be presented more often than expected by chance 
for most alleles of MHC-I and II. 
We confirmed the presentation of TMH-derived peptides 
by re-analysis of peptides from The Immune Epitope Database (IEDB) \citep{vita2019immune}.
Second, we tested our hypothesis that TMHs 
are more evolutionary conserved than soluble protein regions.
Our analysis of human single nucleotide polymorphisms (SNPs) showed 
that random point mutations are indeed less likely
to occur within TMHs. 
These findings strengthen the emerging notion 
that TMHs are important for the T cell-mediated adaptive immune system, 
and hence are of importance in vaccine development.

@@

To obtain experimental confirmation that peptides stemming from TMHs 
are presented by MHC-I and MHC-II,
we mined the IEDB \citep{vita2019immune}
for confirmed human MHC-ligands.
We queried the IEDB for all linear epitopes obtained
from MHC ligand assays in healthy humans, 
carrying the MHC alleles as used in this study.
From these epitopes, we kept those that were present
exactly once in the human reference proteome
with UniProt ID UP000005640\_9606.
We concluded that the epitope overlapped with a TMH if at least 1 amino acid was overlapping with a TMH, as predicted with \verb;TMHMM; \cite{krogh2001predicting}.
The full analysis can be found
at \url{https://github.com/richelbilderbeek/bbbq_article_issue_157}.

@@

@@

@@

@@

FB is funded by a Veni grant from the Netherlands Organization for Scientific
Research (016.Veni.192.026) and an Off-Road Grant from the Dutch Medical Science Foundation (ZonMW 04510011910005).
GvdB is funded by a Young Investigator Grant from 
the Human Frontier Science Program (HFSP; RGY0080/2018), 
and a Vidi grant from 
the Netherlands Organization for Scientific Research (NWO-ALW VIDI 864.14.001). 
GvdB has received funding from the European Research Council (ERC) 
under the European Union’s Horizon 2020 research and 
innovation programme (grant agreement No. 862137).

@@

@@

\section*{Supplemental Data}

%\href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.
